---
title: "Onny Visual Raja Ampat Comparisons"
author: "Zack Gold"
date: "04/15/2021"
output: html_document
---

Load Packages
```{r}
library(here)
library(tidyverse)
library(phyloseq)
library(metagMisc)
```

# Load Data
### Visual Survey Data
```{r}
#Visual Survery Data
visual <- read.table(file= here("data","20201228_raja_ampat_data_visual_census_FIX_zjg.txt"), header=T, sep="\t")

visual %>% 
  pivot_longer( cols=`Anitas_Garden`:`WEST_MANSUAR`, names_to ="Site", values_to ="Presence") %>% 
  dplyr::select(Visual_Species =ScientificName_accepted, Visual_Family = Family, Visual_Genus=Genus, Site, Presence) -> visual_data

visual_data$Visual_Species %>% unique() %>%  length()
```

### eDNA Data
```{r}
#eDNA Data
physeq_asv_site_viz <- readRDS(, file=here( "data", "physeq_asv_site_viz.RDS"))

subset_samples(physeq_asv_site_viz, Region=="Raja Ampat") -> phy_raj

phy_raj = filter_taxa(phy_raj, function(x) sum(x) > 0, TRUE)


phyloseq_to_df(phy_raj) %>% 
  pivot_longer( cols=`Anitas_Garden`:`WEST_MANSUAR`, names_to ="Site", values_to ="nReads") -> eDNA_data


```

### CRUX Data

```{r}

#Visual Survery Data
crux <- read.table(file= here("data","global_database_taxonomy_20201204.csv"), header=T, sep=",")



```

# Comparison of Visual and eDNA Data

### ASVs per Site

```{r}
eDNA_data %>% 
  filter(., nReads >0) %>% 
  group_by(Site) %>% 
  dplyr::summarise(ASV_Count = n_distinct(OTU), Species_count = n_distinct(Species)) -> ASV_counts

```
### Species Per Site
```{r}
eDNA_data %>% 
  filter(., nReads >0) %>% 
   filter(., !Species %in% c("","NA sp.")) %>% 
  group_by(Site) %>% 
  dplyr::summarise(Species_Count = n_distinct(Species)) -> Species_counts

```
### Species Per Site Visual
```{r}

visual_data %>% 
  filter(., Presence >0) %>% 
  group_by(Site) %>% 
  dplyr::summarise(Species_Count_Viz = n_distinct(Visual_Species)) -> Visual_Species_counts

```
```{r}
ASV_counts %>% 
  left_join(Visual_Species_counts) %>% 
  mutate(., perc = ASV_Count/Species_Count_Viz) %>% 
  filter(., Site != "KABUI_STRAIT") %>% 
  dplyr::summarise(mean(perc))
```


### Region
##### Species
```{r}

eDNA_visual_region_overlap<- intersect(eDNA_data$Species, visual_data$Visual_Species)

eDNA_region_unique<- setdiff(eDNA_data$Species, visual_data$Visual_Species)
eDNA_region_unique[!eDNA_region_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_region_unique

viz_region_unique<- setdiff(visual_data$Visual_Species,eDNA_data$Species)

length(eDNA_region_unique)/(length(eDNA_visual_region_overlap) + length(eDNA_region_unique))

eDNA_data %>% 
  filter(Species %in% eDNA_region_unique) %>% 
  dplyr::summarise(n_distinct(Family),n_distinct(Genus))

eDNA_region_unique %>% 
  sort()
```
##### How many Species Only Observed via Visual Surveys have 12S MiFish Barcodes?
```{r}

viz_species_with_barcode <- intersect(viz_region_unique, crux$Species)
viz_species_without_barcode <- setdiff(viz_region_unique, crux$Species)

```

##### Genus
```{r}

eDNA_visual_region_genus_overlap<- intersect(eDNA_data$Genus, visual_data$Visual_Genus)

eDNA_region_unique_genus<- setdiff(eDNA_data$Genus, visual_data$Visual_Genus)
eDNA_region_unique_genus[!eDNA_region_unique_genus %in% c("","NA sp.","Engraulis mordax")] ->eDNA_region_unique_genus

viz_region_unique_genus<- setdiff(visual_data$Visual_Genus,eDNA_data$Genus)


```

##### Family
```{r}

eDNA_visual_region_family_overlap<- intersect(eDNA_data$Family, visual_data$Visual_Family)

eDNA_region_unique_family<- setdiff(eDNA_data$Family, visual_data$Visual_Family)
eDNA_region_unique_family[!eDNA_region_unique_family %in% c("","NA sp.","Engraulis mordax")] ->eDNA_region_unique_family

viz_region_unique_family<- setdiff(visual_data$Visual_Family,eDNA_data$Family)


```

##### Species
```{r}

eDNA_visual_region_overlap<- intersect(eDNA_data$Species, visual_data$Visual_Species)

eDNA_region_unique<- setdiff(eDNA_data$Species, visual_data$Visual_Species)
eDNA_region_unique[!eDNA_region_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_region_unique

viz_region_unique<- setdiff(visual_data$Visual_Species,eDNA_data$Species)

length(eDNA_region_unique)/(length(eDNA_visual_region_overlap)+length(viz_region_unique))


```
### Site Specific
```{r}
eDNA_data %>% 
  filter(., Site=="Anitas_Garden") %>% 
  filter(., nReads >0) -> eDNA_data_AG

eDNA_data %>% 
  filter(., Site=="CAPE_KRI") %>% 
  filter(., nReads >0) -> eDNA_data_CK


eDNA_data %>% 
  filter(., Site=="KABUI_STRAIT") %>% 
  filter(., nReads >0) -> eDNA_data_KS


eDNA_data %>% 
  filter(., Site=="KRI_LAGOON") %>% 
  filter(., nReads >0) -> eDNA_data_KL

eDNA_data %>% 
  filter(., Site=="MELISSAS_GARDEN") %>% 
  filter(., nReads >0) -> eDNA_data_MG

eDNA_data %>% 
  filter(., Site=="SARDINE_REEF") %>% 
  filter(., nReads >0) -> eDNA_data_SR

eDNA_data %>% 
  filter(., Site=="SECRET_LAGOON") %>% 
  filter(., nReads >0) -> eDNA_data_SL

eDNA_data %>% 
  filter(., Site=="WEST_MANSUAR") %>% 
  filter(., nReads >0) -> eDNA_data_WM


```

```{r}
visual_data %>% 
  filter(., Site=="Anitas_Garden") %>% 
  filter(., Presence >0) -> viz_data_AG

visual_data %>% 
  filter(., Site=="CAPE_KRI") %>% 
  filter(., Presence >0) -> viz_data_CK


visual_data %>% 
  filter(., Site=="KABUI_STRAIT") %>% 
  filter(., Presence >0) -> viz_data_KS


visual_data %>% 
  filter(., Site=="KRI_LAGOON") %>% 
  filter(., Presence >0) -> viz_data_KL

visual_data %>% 
  filter(., Site=="MELISSAS_GARDEN") %>% 
  filter(., Presence >0) -> viz_data_MG

visual_data %>% 
  filter(., Site=="SARDINE_REEF") %>% 
  filter(., Presence >0) -> viz_data_SR

visual_data %>% 
  filter(., Site=="SECRET_LAGOON") %>% 
  filter(., Presence >0) -> viz_data_SL

visual_data %>% 
  filter(., Site=="WEST_MANSUAR") %>% 
  filter(., Presence >0) -> viz_data_WM
```

##### Anitas Garden
```{r}
# Total ASVs
eDNA_data_AG$OTU %>%  unique() %>%  length()
#Total Species
eDNA_data_AG$Species %>%  unique() %>%  length()

eDNA_visual_AG_overlap<- intersect(eDNA_data_AG$Species, viz_data_AG$Visual_Species)

eDNA_AG_unique<- setdiff(eDNA_data_AG$Species, viz_data_AG$Visual_Species)
eDNA_AG_unique[!eDNA_AG_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_AG_unique

viz_AG_unique<- setdiff(viz_data_AG$Visual_Species,eDNA_data_AG$Species)

length(eDNA_visual_AG_overlap)/(length(eDNA_visual_AG_overlap)+length(eDNA_AG_unique)+length(viz_AG_unique))
length(eDNA_AG_unique)/(length(eDNA_visual_AG_overlap)+length(eDNA_AG_unique))

(length(eDNA_AG_unique) + length(viz_AG_unique) + length(eDNA_visual_AG_overlap))/ (length(viz_AG_unique)+length(eDNA_visual_AG_overlap)) -> average_increase_AG
```

##### CAPE_KRI
```{r}

eDNA_visual_CK_overlap<- intersect(eDNA_data_CK$Species, viz_data_CK$Visual_Species)

eDNA_CK_unique<- setdiff(eDNA_data_CK$Species, viz_data_CK$Visual_Species)
eDNA_CK_unique[!eDNA_CK_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_CK_unique

viz_CK_unique<- setdiff(viz_data_CK$Visual_Species,eDNA_data_CK$Species)

length(eDNA_visual_CK_overlap)/(length(eDNA_visual_CK_overlap)+length(eDNA_CK_unique)+length(viz_CK_unique))
length(eDNA_CK_unique)/(length(eDNA_visual_CK_overlap)+length(eDNA_CK_unique))

(length(eDNA_CK_unique) + length(viz_CK_unique) + length(eDNA_visual_CK_overlap))/ (length(viz_CK_unique)+length(eDNA_visual_CK_overlap)) -> average_increase_CK

```

##### KABUI_STRAIT
```{r}

# Total ASVs
eDNA_data_KS$OTU %>%  unique() %>%  length()
#Total Species
eDNA_data_KS$Species %>%  unique() %>%  length()
viz_data_KS$Visual_Species %>%  unique() %>%   length()
eDNA_visual_KS_overlap<- intersect(eDNA_data_KS$Species, viz_data_KS$Visual_Species)

eDNA_KS_unique<- setdiff(eDNA_data_KS$Species, viz_data_KS$Visual_Species)
eDNA_KS_unique[!eDNA_KS_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_KS_unique

viz_KS_unique<- setdiff(viz_data_KS$Visual_Species,eDNA_data_KS$Species)

length(viz_KS_unique) + length(eDNA_visual_KS_overlap)
length(eDNA_KS_unique)
  
length(eDNA_visual_KS_overlap)/(length(eDNA_visual_KS_overlap)+length(eDNA_KS_unique)+length(viz_KS_unique))

length(eDNA_KS_unique)/(length(eDNA_visual_KS_overlap)+length(eDNA_KS_unique))

(length(eDNA_KS_unique) + length(viz_KS_unique) + length(eDNA_visual_KS_overlap))/ (length(viz_KS_unique)+length(eDNA_visual_KS_overlap)) -> average_increase_KS

```

##### KRI_LAGOON
```{r}

# Total ASVs
eDNA_data_KL$OTU %>%  unique() %>%  length()
#Total Species
eDNA_data_KL$Species %>%  unique() %>%  length()


eDNA_visual_KL_overlap<- intersect(eDNA_data_KL$Species, viz_data_KL$Visual_Species)

eDNA_KL_unique<- setdiff(eDNA_data_KL$Species, viz_data_KL$Visual_Species)
eDNA_KL_unique[!eDNA_KL_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_KL_unique

viz_KL_unique<- setdiff(viz_data_KL$Visual_Species,eDNA_data_KL$Species)

length(eDNA_visual_KL_overlap) +length(viz_KL_unique)


length(eDNA_visual_KL_overlap)/(length(eDNA_visual_KL_overlap)+length(eDNA_KL_unique)+length(viz_KL_unique))

length(eDNA_KL_unique)/(length(eDNA_visual_KL_overlap)+length(eDNA_KL_unique))

(length(eDNA_KL_unique) + length(viz_KL_unique) + length(eDNA_visual_KL_overlap))/ (length(viz_KL_unique)+length(eDNA_visual_KL_overlap)) -> average_increase_KL


```

##### MELISSAS_GARDEN
```{r}

eDNA_visual_MG_overlap<- intersect(eDNA_data_MG$Species, viz_data_MG$Visual_Species)

eDNA_MG_unique<- setdiff(eDNA_data_MG$Species, viz_data_MG$Visual_Species)
eDNA_MG_unique[!eDNA_MG_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_MG_unique

viz_MG_unique<- setdiff(viz_data_MG$Visual_Species,eDNA_data_MG$Species)

length(eDNA_visual_MG_overlap)/(length(eDNA_visual_MG_overlap)+length(eDNA_MG_unique)+length(viz_MG_unique))

length(eDNA_MG_unique)/(length(eDNA_visual_MG_overlap)+length(eDNA_MG_unique))

(length(eDNA_MG_unique) + length(viz_MG_unique) + length(eDNA_visual_MG_overlap))/ (length(viz_MG_unique)+length(eDNA_visual_MG_overlap)) -> average_increase_MG

```
##### SARDINE_REEF
```{r}

eDNA_visual_SR_overlap<- intersect(eDNA_data_SR$Species, viz_data_SR$Visual_Species)

eDNA_SR_unique<- setdiff(eDNA_data_SR$Species, viz_data_SR$Visual_Species)
eDNA_SR_unique[!eDNA_SR_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_SR_unique

viz_SR_unique<- setdiff(viz_data_SR$Visual_Species,eDNA_data_SR$Species)

length(eDNA_visual_SR_overlap)/(length(eDNA_visual_SR_overlap)+length(eDNA_SR_unique)+length(viz_SR_unique))

length(eDNA_SR_unique)/(length(eDNA_visual_SR_overlap)+length(eDNA_SR_unique))

(length(eDNA_SR_unique) + length(viz_SR_unique) + length(eDNA_visual_SR_overlap))/ (length(viz_SR_unique)+length(eDNA_visual_SR_overlap)) -> average_increase_SR


```
##### SECRET_LAGOON
```{r}

eDNA_visual_SL_overlap<- intersect(eDNA_data_SL$Species, viz_data_SL$Visual_Species)

eDNA_SL_unique<- setdiff(eDNA_data_SL$Species, viz_data_SL$Visual_Species)
eDNA_SL_unique[!eDNA_SL_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_SL_unique

viz_SL_unique<- setdiff(viz_data_SL$Visual_Species,eDNA_data_SL$Species)

length(eDNA_visual_SL_overlap)/(length(eDNA_visual_SL_overlap)+length(eDNA_SL_unique)+length(viz_SL_unique))

length(eDNA_SL_unique)/(length(eDNA_visual_SL_overlap)+length(eDNA_SL_unique))

(length(eDNA_SL_unique) + length(viz_SL_unique) + length(eDNA_visual_SL_overlap))/ (length(viz_SL_unique)+length(eDNA_visual_SL_overlap)) -> average_increase_SL

```

##### WEST_MANSUAR
```{r}

eDNA_visual_WM_overlap<- intersect(eDNA_data_WM$Species, viz_data_WM$Visual_Species)

eDNA_WM_unique<- setdiff(eDNA_data_WM$Species, viz_data_WM$Visual_Species)
eDNA_WM_unique[!eDNA_WM_unique %in% c("","NA sp.","Engraulis mordax")] ->eDNA_WM_unique

viz_WM_unique<- setdiff(viz_data_WM$Visual_Species,eDNA_data_WM$Species)

length(eDNA_visual_WM_overlap)/(length(eDNA_visual_WM_overlap)+length(eDNA_WM_unique)+length(viz_WM_unique))

(length(eDNA_WM_unique) + length(viz_WM_unique) + length(eDNA_visual_WM_overlap))/ (length(viz_WM_unique)+length(eDNA_visual_WM_overlap)) -> average_increase_WM

```
### mean
```{r}
mean(c(length(eDNA_WM_unique)/(length(eDNA_visual_WM_overlap)+length(eDNA_WM_unique)),
     length(eDNA_SL_unique)/(length(eDNA_visual_SL_overlap)+length(eDNA_SL_unique)),
     length(eDNA_SR_unique)/(length(eDNA_visual_SR_overlap)+length(eDNA_SR_unique)),
     length(eDNA_MG_unique)/(length(eDNA_visual_MG_overlap)+length(eDNA_MG_unique)),
     length(eDNA_KL_unique)/(length(eDNA_visual_KL_overlap)+length(eDNA_KL_unique)),
     length(eDNA_KS_unique)/(length(eDNA_visual_KS_overlap)+length(eDNA_KS_unique)),
     length(eDNA_AG_unique)/(length(eDNA_visual_AG_overlap)+length(eDNA_AG_unique)),
     length(eDNA_CK_unique)/(length(eDNA_visual_CK_overlap)+length(eDNA_CK_unique)))

     )


mean(c((length(eDNA_AG_unique) + length(viz_AG_unique) + length(eDNA_visual_AG_overlap))/ (length(viz_AG_unique)+length(eDNA_visual_AG_overlap)),
     (length(eDNA_KS_unique) + length(viz_KS_unique) + length(eDNA_visual_KS_overlap))/ (length(viz_KS_unique)+length(eDNA_visual_KS_overlap)),
     (length(eDNA_KL_unique) + length(viz_KL_unique) + length(eDNA_visual_KL_overlap))/ (length(viz_KL_unique)+length(eDNA_visual_KL_overlap)),
     (length(eDNA_CK_unique) + length(viz_CK_unique) + length(eDNA_visual_CK_overlap))/ (length(viz_CK_unique)+length(eDNA_visual_CK_overlap)),
     (length(eDNA_MG_unique) + length(viz_MG_unique) + length(eDNA_visual_MG_overlap))/ (length(viz_MG_unique)+length(eDNA_visual_MG_overlap)),
     (length(eDNA_SR_unique) + length(viz_SR_unique) + length(eDNA_visual_SR_overlap))/ (length(viz_SR_unique)+length(eDNA_visual_SR_overlap)),
     (length(eDNA_SL_unique) + length(viz_SL_unique) + length(eDNA_visual_SL_overlap))/ (length(viz_SL_unique)+length(eDNA_visual_SL_overlap)),
     (length(eDNA_WM_unique) + length(viz_WM_unique) + length(eDNA_visual_WM_overlap))/ (length(viz_WM_unique)+length(eDNA_visual_WM_overlap))))

```

```{r}

eDNA_data %>% 
  filter(., Species !="") %>% 
  dplyr::select(Species, Site, nReads) %>% 
  group_by(Species, Site) %>% 
  summarise(., nReads = sum(nReads)) %>% 
   full_join(visual_data, by=c("Species"="Visual_Species", "Site")) %>% 
   mutate(., Detection=case_when(nReads > 0 & Presence > 0 ~"Both Detected",
                       nReads > 0 & is.na(Presence) | Presence == 0 ~ "eDNA Detection Only",
                       Presence == 0 | is.na(Presence) & nReads == 0 | is.na(nReads) ~ "Both Not Detected",
                       Presence > 0 & nReads == 0 | is.na(nReads) ~"Visual Detection Only",
                       TRUE ~"BROKEN")) %>% 
  dplyr::select(Species, Site, Detection) %>%  distinct() -> combined_df

combined_df %>%  View()
combined_df %>% 
  group_by(Species) %>% 
  count(Detection) %>% 
  filter(., Detection %in% "Both Detected") -> both_detected

combined_df %>% 
  pivot_wider(., names_from = Site, values_from = Detection) %>% 
  mutate(., Both_Detected_Across_Raja_Ampat = if_else( Species %in% both_detected$Species, "Concurrently Detected", "Not Concurrently Detected")) -> cleaned_combined


cleaned_combined %>% write_csv(file = here("data","eDNA_vs_allen_supplemental_table.csv"))


eDNA_data %>% dplyr::select(Domain  ,  Phylum ,  Class   ,   Order    ,    Family    , Genus ,    Species) %>%  distinct() -> taxonomy 

eDNA_data %>% 
  filter(., Species !="") %>% 
  dplyr::select(Species, Site, nReads) %>% 
  group_by(Species) %>% 
  summarise(., nReads = sum(nReads)) %>% 
  filter(., !Species %in% visual_data$Visual_Species) %>% 
  dplyr::select(Species) %>%  left_join( taxonomy) %>% write_csv(file = here("data","eDNA_only_supplemental_table_taxonomy.csv"))
```
